Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-13 paper/paper.tex
work in progress Tested everything on quipu.

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500-exact}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-plot--p-300-50-0-0-1500-full_array}
  \caption{Countour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space as guassians with
    characteristic length equal to the Abbe diffraction limit of
    $600nm$ wavelength light (ends up being about 200nm)\fixme{say
      something about the axial resolution, which is even more limited
      than the lateral resolution, which is why we integrate data long
      axial direction}}
  \label{image-p}
\end{figure*}

@@

This simple cell shape is a good starting point for observing in
detail the dynamic interaction between the different stages of protein
that lead to their qualitatively distinct behavoir. Figure
\ref{image-p} shows the process in a series of frames taken from
simulation animations for both the deterministic and stochastic
simulations.  The stochastic concentrations have been 'smeared out' in
a manner meant to reproduce the images shown by a diffraction limited
microscope.  The protein densities which are located at specific grid
points give light to sorrounding grid points with a guassian weighting
function that has a variance equal to the Abbe diffraction limit of
$600nm$ wavelength light.  Each frame is 2.5 seconds ahead of the
last, and each image shows a the concentration of a given state of
protein summed over the coordinate orthogonal to the page.  The color
scale for each protein state is set according to the maximum values
observed.

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500-exact}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-plot--p-300-50-0-0-1500-full_array}
  \caption{Countour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

This simple cell shape is a good starting point for observing in
detail the dynamic interaction between the different stages of protein
that lead to their qualitatively distinct behavoir. Figure
\ref{image-p} shows the process in a series of frames taken from
simulation animations for both the deterministic and stochastic
simulations.  We have 'smeared out' the stochastic concentrations in a
manner meant to reproduce the images shown by diffraction limited
flourescence microscopy.  We do so using the two dimensional gaussian
approximation developed by Zhang et all~\cite{zhang2007gaussian}.  In
this approximation we use a numerical aperture value of 1.3, which is
the same as used by mannik experimentally, and a wavelength of
$509nm$, typical of green flourescent microscopy.  Each frame is 2.5
seconds ahead of the last, and each image shows a the concentration of
a given state of protein summed over the coordinate orthogonal to the
page.  The color scale for each protein state is set according to the
maximum values observed.
